\LARGE \bf Artificial Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-06-30 paper.tex
Update on Overleaf.

\emph{Effort balancing and human desires}: avoids plans where efforts are
not fairly distributed among the agents taking part to the plan.  It is
indeed sometimes beneficial to balance efforts between the human and
the robot,

\emph{Simplicity}: avoids plans with too many interdependencies
between the actions of agents mentioned in the plan, as a problem with
executing just one of those actions could invalidate the entire
plan. Also intricate human-robot activity may cause discomfort since
the human will find himself repeatedly in a situation where his is
waiting for the robot to act,

>>>>

\emph{Effort balancing with respect of human desires}: avoids plans where efforts are
not distributed among the agents taking part to the plan following the human preferences.  It is
indeed sometimes beneficial to balance efforts between the human and
the robot. Sometimes the human wants to do more or, on the contrary, prefers to leave the 
robot do all what it can.

\emph{Simplicity}: promotes plans that limit  too many interdependencies
between the actions of agents mentioned in the plan, as a problem with
executing just one of those actions could invalidate the entire
plan. Also intricate human-robot activity may cause discomfort since
the human will find himself repeatedly in a situation where his is
waiting for the robot to act,
